What do incoming university students believe about open science practices in

### 2021-05-11 analysis/Manuscript.Rmd
tidy up the correlation chunk

# breadcrumbs: keep the values that I need from this tibble
# use p_tidy? to clean up the pvalues {done!}
# round the corr & CI {done!}
# join with the practice_means tibble & turn into a table {done!}
# need to figure out whether I can rotate a page in papaja

# just keeping this here for now, but will be able to delete
# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
# 
# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
# 
# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
# 
# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
# 
# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
# 
# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
# 
# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
# 
# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
# 
# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)

# breadcrumbs: 
# I need to use apa_tables.... (in line with papaja)
# pull means & sd into the same column with (sd) in parentheses [done!]
# headings should then be norm, counternorm, difference [done!]
# add correlations with 95% CIs 
# update practice descriptions so they make sense to readers

>>>>

# breadcrumbs:
# need to figure out whether I can rotate a page in papaja
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers
